---
title: "Report on modeling of excise manner"
author: "HAN LONG"
date: '2015-01-13'
output: html_document
---
### Abstract
The goal of your project is to predict the manner in which they did the exercise. This is the 'classe" variable in the training set.

---
### Prepare data
#### 1. Download/Import Data
```{r eval=FALSE}
library(RCurl)
trainingFile <- getURL('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv')
testingFile  <- getURL('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv')
```
```{r}
setwd('/Users/longhan/Documents/cousera/learning/001predictionMotivation')
training.raw  <- read.csv('./pml-training.csv', na.strings=c('', 'NA', 'NULL'))
testing.raw   <- read.csv('./pml-testing.csv', na.strings=c('', 'NA', 'NULL'))
training.clean <- training.raw[ , colSums(is.na(training.raw)) == 0]
dim(training.raw)
```

### 2. Filter unrelated columns
First filter out the columns with NA values. Then, filter out the most likely not related columns as X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window. 
```{r}
no_na_column <- training.raw[ , colSums(is.na(training.raw)) == 0]
tobe_removed = c('X', 'user_name', 'raw_timestamp_part_1', 'raw_timestamp_part_2', 'cvtd_timestamp', 'new_window', 'num_window')
training.clean <- no_na_column[, -which(names(no_na_column) %in% tobe_removed)]
testing.clean  <- testing.raw[ , which(names(testing.raw) %in% names(training.clean))]
dim(training.clean)
dim(testing.clean)
```

### 3. Modeling
Before modeling we should create partitions for validation. And the library caret is used here.
```{r}
library(caret)
trainingIndex  <- createDataPartition(training.clean$classe, p=.60, list=FALSE)
training.train <- training.clean[ trainingIndex,]
training.valid <- training.clean[-trainingIndex,]
```
Here, the randomForest is applied to find the classification model with training.train data set.
```{r}
library(randomForest)
rfModel <- randomForest(classe~.,data=training.train)
print(rfModel)
```
And proceed with the verification of variable importance measures as produced by random Forest, validation is also applied on traing.valid data set.
```{r}
importance(rfModel)
cfMat <- confusionMatrix(predict(rfModel,newdata=training.valid), training.valid$classe)
cfMat
```
And it is found that the accuracy on training set is `r unname(cfMat$overall[1])`.

### 4. Predict
Now we have got the model for predict on the testing data.
```{r}
predict(rfModel,newdata=testing.clean)
```